---
title: "EricFriesth_hw2"
author: "Eric Friesth"
date: "9/25/2019"
output: html_document
---

## https://github.com/ericf8/ds202_hw2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

https://github.com/ericf8/ds202_hw2

## Part 1

1. This color issue can be easily solved by moving "colour = "blue"" outside the aes()

ggplot(mpg, aes(displ, hwy)) + geom_point(colour = "blue", aes()) + ggtitle("Scatter with Blue Points")

```{r}

library(ggplot2)

ggplot(mpg, aes(displ, hwy)) + geom_point(colour = "blue", aes()) + labs(title="Scatter with Blue Points")

```

2. 

```{r}

#Call tidyverse from library to make sure I have everything and it's all up to date
library(tidyverse)
#Call classdata from library to make sure I have everything and it's all up to date
library(classdata)

#Create a subset of fbiwide with the condition that it is every state except California
notCali = subset(fbiwide, fbiwide$State != "California") 

#Create a subset of fbiwide with the condition that it is on the state California
cali = subset(fbiwide, fbiwide$State == "California")

#Create a plot with two separate geom_lines
ggplot(data = notCali) + geom_line(aes(x = Year, y = Motor.vehicle.theft, group = notCali$State), colour = "dark turquoise") + geom_line(data = cali, aes(x = Year, y = Motor.vehicle.theft, group = cali$State), colour = "red") + labs(title="Motor vehicle theft over time", x="Year", y="Motor Vehicle Thefts") 

#Would like some help on how to set up a legend. My partner Ash and I looked all over stackoverflow, reddit, and rstudio documentation and couldn't get it to work. So sorry about that.
```

3. 

```{r}

#To get the boxes to work, you first are able to remove the coord flip and place the variable and log count within the aes()
ggplot(fbi, aes(fbi$Violent.crime, log(Count))) + geom_boxplot() + labs(title = "Boxplot of Violent Crimes", x = "Violent Crime", y = "Count")

```

4. 

```{r}

#Found a rstudio tutorial that showed me that we are able to facet wrap using displ as long as the variables and dataset used are correctly defined
ggplot(mpg) + geom_point(aes(x = cyl, y = hwy)) + facet_wrap(~displ)

```

## Part 2

```{r}
ggplot(mpg, aes(cty, hwy)) + geom_point()

```

5. For one small issue with this plot, it's not labelled well (x and y as well as a meaningful title). I propose adding labels as well as group/color this plot by Manufacturer.

ggplot(mpg, aes(cty, hwy, color = mpg$manufacturer)) + geom_point() + labs(title = "City vs Highway MPG", x="City MPG", y="Highway MPG")

```{r}

ggplot(mpg, aes(cty, hwy, color = mpg$manufacturer)) + geom_point() + labs(title = "City vs Highway MPG", x="City MPG", y="Highway MPG")

```

6. Based on this plot, the average mpgs of cars in the 1999s had a higher mpg.

```{r}

#Created a variable for average mpg by adding the city and highway mpgs together and dividing by 2
avgMPG = (mpg$cty + mpg$hwy) / 2

#scatter plotted the data to show the model vs their average mpg by the years 1999 and 2008
#ggplot(mpg, aes(avgMPG, class, color = year)) + geom_point() + labs(title = "Average MPG of Classes of Cars by Year", x="Average MPG", y="Class/Model of Car")

cars1999 = subset(mpg, year == 1999)
cars2008 = subset(mpg, year == 2008)


```

7. The distribution of Price on the Dataset Diamonds is positively skewed and the scatter plot shows a slightly positive correlation between Price and Carat. 

```{r}

# Created a histogram showing the distribution of diamonds prices displaying the cut as well.
ggplot(diamonds, aes(price, fill = cut)) + geom_histogram(bins = 54000, binwidth = 600) + labs(title = "Distribution of Diamond Prices by Cut", x = "Price (USD)", y = "Frequency")

# Created a scatter plot showing the price by carat.
ggplot(diamonds, aes(carat, price, group = clarity)) + geom_point() + labs(title= "Price of Diamond by its Carat", x="Carat", y="Price")

# Displayed just the nonlinear regressions to show the trend of the Price of a diamond by its carat and its clarity.
ggplot(diamonds, aes(carat, price, color = clarity, group = clarity)) + labs(title= "Price of Diamond by its Carat", x="Carat", y="Price") + geom_smooth()

```

